### 2016-09-02 notions.tex
cheers

\heading{Comparison to Naor-Yogev definition.}
The style of the Naor-Yogev (NY) definition is slightly different. \jnote{Even if we ignore
all the other issues, chief among them the inconsistent way it treats the hash functions.}
Lifting their definition to our setting, the experiment is similar but the attacker
succeeds only if it outputs a single query $q$ for which $\Qry( M,
\aux, q) \neq q(S)$  \emph{subject to the restriction that it did not query $q$ to its $\Qry$ oracle}.
It will be interesting to understand formally the relation between our definition and theirs.
Here are some observations:
\begin{enumerate}
\item Say a scheme is $\epsilon_{NY}$-secure under the NY definition.
Then we claim it is $(t,q, r, q\epsilon_{NY}/r)$-correct. To see
this, assume not. Then there is a $t$-time attacker~$A$ that, with
probability at least $\epsilon'=q\epsilon_{NY}/r$,
issues~$q$ Test-queries of which at least~$r$ cause errors. If we simply run~$A$ and then choose a random Test-query to
output, we succeed with probability at least $\epsilon' \cdot r/q$. It is unclear whether this is tight.

@@

%\jnote{Actually, I am unsure whether a one-wayness definition is independently
%interesting if we have (and can achieve) a semantic-security definition.}
%\tsnote{Depends on what information we decide is okay to leak.  A
%  classical BF gives an~$M$ that leaks a good approximation of $|S|$.
%Do we want that to be considered semantically secure?  On the other
%hand, a classical BF is one-way in the ROM, up to the min-entropy of
%the distribution over~$S$.  So that may already give an interesting
%example that fits in the gap.} \jnote{Yes. Semantic security
%is parameterized by the leakage function, and so might or might not imply
%one-wayness.}
Our semantic-secure definition is simulation-based (see
Figure~\ref{fig:privacy-ss}).
In this definition we compare the probabilities with which an attacker $A$ outputs~1
in two experiments: one ``real'' and one ``simulated.''
In the real experiment (ss-rep-1), $A$ outputs a set $S$ and is given the
public information $\pubaux$ that results from running $\Rep(S)$.\footnote{We do not give $A$ an oracle for
issuing queries; since $A$ knows the set~$S$, such an oracle would be superfluous.
\jnote{Interestingly,
if we provided a query oracle in the real world and an oracle that returns the correct
answer in the simulated world, then the definition seems to imply
correctness also.}}
\tsnote{Need to pass state between stages if you want~$A$ to know the
  set it previously sampled, right?} \jnote{Yes, unless by convention all algorithms
  are stateful. (smiley face). Whatever you prefer is fine with me.}
In the simulated experiment (ss-rep-0), $A$ outputs $S$ and is given $\pubaux$ output
by a simulator $\Sim$ that is only given ${\sf leak}(S)$ for some (possibly randomized)
function~${\sf leak}$. \jnote{Could also give $\Sim$ a membership oracle.}
For a given function ${\sf leak}$, adversary $A$, and simulator~$\Sim$,
we define the advantage measure
$\AdvPrivSS{\Pi,{\sf leak}}{A,\Sim} \bydef
\left| \Prob{\ExpPrivSSreal{\Pi}{A}=1} -
\Prob{\ExpPrivSSsim{\Pi,{\sf leak}}{A, \Sim}=1} \right|$.
Informally, a scheme $\Pi$ is secure with respect to some leakage function ${\sf leak}$
if for all $A$ there is a simulator $\Sim$ such that
$\AdvPrivSS{\Pi,{\sf leak}}{A,\Sim}$ is small.
Intuitively, this means that the public portion
$\pubaux$ of the representation of a set~$S$ leaks~${\sf leak}(S)$ and nothing more.
\jnote{Need to relate running time of $\Sim$ to running time of~$A$.}

\begin{figure}[hbtp]
\centering
\fpage{.6}{
\hpagess{.5}{.45}
{
\experimentv{$\ExpPrivSSreal{\Pi}{A}$}\\
$S \getsr A()$ \\
$(M,\pubaux,\privaux) \getsr \Rep(S)$\\
return $A(M,\pubaux)$\\
}
%
{
\experimentv{$\ExpPrivSSsim{\Pi, {\sf leak}}{A, \Sim}$}\\
$S \getsr A()$\\
$(M,\pubaux) \getsr \Sim({\sf leak}(S))$ \\
return $A(M,\pubaux)$\\

>>>>

\heading{Comparison to Naor-Yogev definition.}
The style of the Naor-Yogev (NY) definition is slightly different. \jnote{Even if we ignore
all the other issues, chief among them the inconsistent way it treats the hash functions.}
Lifting their definition to our setting, the experiment is similar but the attacker
succeeds only if it outputs a single query $q$ for which $\Qry(\pubaux,\privaux, q) \neq q(S)$  \emph{subject to the restriction that it did not query $q$ to its $\Qry$ oracle}.
It will be interesting to understand formally the relation between our definition and theirs.
Here are some observations:
\begin{enumerate}
\item Say a scheme is $\epsilon_{NY}$-secure under the NY definition.
Then we claim it is $(t,q, r, q\epsilon_{NY}/r)$-correct. To see
this, assume not. Then there is a $t$-time attacker~$A$ that, with
probability at least $\epsilon'=q\epsilon_{NY}/r$,
issues~$q$ Test-queries of which at least~$r$ cause errors. If we simply run~$A$ and then choose a random Test-query to
output, we succeed with probability at least $\epsilon' \cdot r/q$. It is unclear whether this is tight.

@@

%\jnote{Actually, I am unsure whether a one-wayness definition is independently
%interesting if we have (and can achieve) a semantic-security definition.}
%\tsnote{Depends on what information we decide is okay to leak.  A
%  classical BF gives an~$M$ that leaks a good approximation of $|S|$.
%Do we want that to be considered semantically secure?  On the other
%hand, a classical BF is one-way in the ROM, up to the min-entropy of
%the distribution over~$S$.  So that may already give an interesting
%example that fits in the gap.} \jnote{Yes. Semantic security
%is parameterized by the leakage function, and so might or might not imply
%one-wayness.}
Our semantic-secure definition is simulation-based (see Figure~\ref{fig:privacy-ss}).
In this definition we compare the probabilities with which an attacker $A$ outputs~1
in two experiments: one ``real'' and one ``simulated.''
In the real experiment (ss-rep-1), $A$ outputs a set $S$  and is given the
public information $\pubaux$ that results from running $\Rep(S)$.
\footnote{We do not give $A$ an oracle for issuing queries; 
since $A$ knows the set~$S$, such an oracle would be superfluous.
\jnote{Interestingly,
if we provided a query oracle in the real world and an oracle that returns the correct
answer in the simulated world, then the definition seems to imply
correctness also.}}
In the simulated experiment (ss-rep-0), $A$ outputs $S$ and is given $\pubaux$ output
by a simulator $\Sim$ that is only given ${\sf leak}(S)$ for some (possibly randomized)
function~${\sf leak}$.
%\tsnote{Need to pass state between stages if you want~$A$ to know the
%  set it previously sampled, right?} \jnote{Yes, unless by convention all algorithms
%  are stateful. (smiley face). Whatever you prefer is fine with me.}
For a given function ${\sf leak}$, adversary $A$, and simulator~$\Sim$,
we define the advantage measure
$\AdvPrivSS{\Pi,{\sf leak}}{A,\Sim} \bydef
\left| \Prob{\ExpPrivSSreal{\Pi}{A}=1} -
\Prob{\ExpPrivSSsim{\Pi,{\sf leak}}{A, \Sim}=1} \right|$.
Informally, a scheme $\Pi$ is secure with respect to some leakage function ${\sf leak}$
if there is a simulator $\Sim$ such that $\AdvPrivSS{\Pi,{\sf leak}}{A,\Sim}$ is small
for all~$A$. Intuitively, this means that the public portion
$\pubaux$ of the representation of a set~$S$ leaks~${\sf leak}(S)$ and nothing more.

\begin{figure}[hbtp]
\centering
\fpage{.6}{
\hpagess{.5}{.45}
{
\experimentv{$\ExpPrivSSreal{\Pi}{A}$}\\
$(S,\st) \getsr A()$ \\
$(\pubaux,\privaux) \getsr \Rep(S)$\\
return $A(\st,\pubaux)$\\
}
%
{
\experimentv{$\ExpPrivSSsim{\Pi, {\sf leak}}{A, \Sim}$}\\
$(S,\st) \getsr A()$\\
$(\st,\pubaux) \getsr \Sim({\sf leak}(S))$ \\
return $A(\st,\pubaux)$\\
